Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks

### 2016-06-11 docs/papers/2016JNCA/2016JNCA.tex
adding storgrid paper

This subsection discuss the computational complexity of the proposed framework, focusing on the main steps, which are the eigenvalues decomposition (EVD), largest eigenvalues analysis, application of MOS scheme and eigen similarity analysis, according to Figure \ref{fig:fig80} and equations presented in Section \ref{sec:prop_getv}.

>>>>

This subsection discusses the computational complexity of the proposed framework, focusing on the main steps, which are the eigenvalues decomposition (EVD), largest eigenvalues analysis, application of MOS scheme and eigen similarity analysis, according to Figure \ref{fig:fig80} and equations presented in Section \ref{sec:prop_getv}.
